%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
%\nonstopm
\usepackage[left=0.8in,top=0.4in,right=0.8in,bottom=0.4in]{geometry} % Document margins
\name{Manasvi Saxena} % Your name
\address{msaxena2@illinois.edu \\ (571)~$\cdot$~442~$\cdot$~1509 \\ \url{www.github.com/msaxena2} }

\usepackage{hologo}
\usepackage{bibentry}

\begin{document}
 \nobibliography{cv}
 \bibliographystyle{unsrt}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Interests}
\item Programming Language Semantics, Runtime Verification, Safe Hybrid Systems, Language Independent Static and Dynamic Analysis
\end{rSection}

\begin{rSection}{Education}
\begin{rSubsection}{Ph.D. Computer Science, University of Illinois -- Urbana Champaign}{Dec 2023}{}{}
\item Relevant Coursework - Advanced Programming Language Semantics, Programming Verification, Embedded Systems Verification
\end{rSubsection}
\begin{rSubsection}{M.S. Computer Science, University of Illinois -- Urbana Champaign}{May 2018}{}{}
\item Relevant Coursework - Formal Methods of Software Development, Runtime Verification, Logic in Computer Science, Computer and Cryptocurrency Security
\end{rSubsection}
\begin{rSubsection}{B.S. Computer Science, University of Illinois -- Urbana Champaign}{May 2015}{}{}
\item Relevant Coursework - Programming Languages and Compilers, Fundamental Algorithms, Theory of Computation, Computer Networking, Artificial Intelligence
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\begin{rSubsection}{Formal Systems Laboratory, University of Illinois}{May 2018 - Present}{Research Assistant}{Urbana, IL}
\item Leading the design and development of the MediK Framework (\url{https://github.com/medik-framework}).
  The core of MediK is a new domain
  specific language for expressing guidelines in medicine formally as finite
  state machines. MediK is a part of a multi year effort to safely capture
  semantics of medical guidelines formally to derive correct-by-construction
  decision support systems for use in healthcare.
\item Lead developer of RV-Monitor, a language independent monitoring
  that supports rich formalisms for expressing properties.
\end{rSubsection}

\begin{rSubsection}{S3 Automated Reasoning Group, Amazon Web Services}{Summer 2021}{Applied Scientist Intern}{}
\item Developed a tool for measuring effectiveness of a test suite against a property expressed in
  RV-Monitor (\url{https://github.com/runtimeverification/rv-monitor}).
\item Tool reported code coverage w.r.t. regions of the code important for an
  RV-Monitor safety specification, helping ensure test suite exercises important
  regions of the codebase, and was optimized to handle millions of lines of highly
  concurrent code.
\end{rSubsection}

\begin{rSubsection}{S3 Automated Reasoning Group, Amazon Web Services (AWS)}{Summer 2020}{Applied Scientist Intern}{}
\item Developed tooling to ensure S3 codebase adhered to desired safety properites such as serializability.
\item Improved RV-Monitor, an academic tool, to handle millions of lines of
  code, and support expressing complex properties relevant to concurrent systems
    such as read after write consistency and serializability efficiently.
\end{rSubsection}

\begin{rSubsection}{Formal Systems Laboratory, University of Illinois}{August 2016 - May 2018}{Researcher Assistant}{Urbana, IL}
\item Implementing a Proof Assistant (called the K Debugger) for the K Semantics Framework.
\item K (\url{https://github.com/kframework/k}) is a rewrite based semantics framework in which programming
languages can be defined using configurations, computations and rules. Proof Assistant will be used to prove program correctness, using the implementation of Matching Logic in K.
\item Implementing the semantics of the ethereum Abstract Binary Interface (ABI) as a part of the KEVM \\
  (\url{http://github.com/kframework/evm-semantics}) project. The KEVM ABI abstraction
  exposes a higher-level language like layer for smart contract verification.
\end{rSubsection}

\begin{rSubsection}{Runtime Verification Inc., Urbana, Illinois}{July 2015 - May 2016}{Software Engineer}{Urbana, IL}
\item Worked on a team developing a dynamic analysis tool for finding undefined behavior in C programs, using formal semantics of C.
\item Worked on improving tool's performance, and evaluated its applications on large codebases.
\end{rSubsection}

\begin{rSubsection}{Formal Systems Laboratory, University of Illinois}{August 2014 - May 2015}{Undergraduate Researcher}{Urbana, IL}
\item Developed a Semantics based Debugger for the K Semantics Framework.
\item Debugger helps users find bugs in formal semantics defined in K. Allows users to step
through the execution of their program, examine the state space, configurations, and rules
among other features.
\end{rSubsection}

\begin{rSubsection}{Coordinated Science Lab, University of Illinois}{Summer 2014}{Undergraduate Researcher}{Urbana, IL}
\item Worked on visualization of a large dataset containing records of faulty medical devices by the Food and Drug Administration (FDA).
\item Created an interactive web application that displays the visualizations using PHP/Javascript.
\end{rSubsection}

\end{rSection}
%------------------------------------------------

\begin{rSection}{Teaching Experience}

\begin{rSubsection}{Teaching Assistant, CS 427}{Fall 2020}{University of Illinois}{Urbana, IL}
\item Helped prepare course materials, and assisted instructor during lectures
  when needed.
\item Held weekly office hours
\end{rSubsection}
\end{rSection}

%\pagebreak

\begin{rSection}{Projects}

\begin{rSubsection}{The MediK Framework}{github.com/medik-framework}{}{}
\item Lead development of the semantics of the MediK language for expressing
  computer interpretable medical guidelines.
\end{rSubsection}

\begin{rSubsection}{RV-Monitor}{github.com/runtimeverification/rv-monitor}{}{}
\item Part of core team that maintains and develops RV-Monitor - a language
  agnostic monitor framework.
\end{rSubsection}

\begin{rSubsection}{KEVM - Semantics of the EVM in K}{github.com/kframework/evm-semantics}{}{}
\item Worked on formalizing the EVM in K. Worked on capturing the semantics of the Ethereum ABI, as
  an extension to the original semantics.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Publications}
    \item \bibentry{kevm-tool}
    \item \bibentry{kevm}
    \item \bibentry{ha-tr}
    \item \bibentry{guth-hathhorn-saxena-rosu-2016-cav}
    \item \bibentry{rv-tutorial}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Technical Skills}
%
%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Programming Languages & Java, Scala, Python, C, C++, OCaml \\
%Miscellaneous & Git, Intellij IDEA, Eclipse, PyCharm,  \hologo{LaTeX} \\
%\end{tabular}
%
%\end{rSection}

\end{document}
